\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-07-31 NAR_DRAFT.tex
new figures

\subsection{Site-specific prior probability of mutation}
The probability which we have denoted $p(m)$ in equation \ref{eqn:2} for compactness is more precisely the joint probability that a mutation has occured $M$, and that it was to allele $m$, which we will denote here $p(m,M)$.
However, $p(m,M)$ is not constant for every site in the genome, and follows a distribution conditional on the genomic context surrounding the site, denoted here $p(m,M | C)$ \bkmcomment{citation for genomic context in general} .
Assuming that $m$ and $M$ are independent conditional on the genomic context, $\mathrm{p}(m,M \mid C) = \mathrm{p}(m \mid C) \mathrm{p}(M \mid C)$, which we can use Bayes' rule to further decompose as

@@

\begin{tiny}
\begin{verbatim}

@@

\end{document}

>>>>

\subsection{Site-specific prior probability of mutation}
The probability which we have denoted $p(m)$ in equation \ref{eqn:2} for compactness is more precisely the joint probability that a mutation has occured $M$, and that it was to allele $m$, which we will denote here $p(m,M)$.
However, $p(m,M)$ is not constant for every site in the genome, and follows a distribution conditional on the genomic context surrounding the site, denoted here $p(m,M | C)$ \cite{Buisson2019}.
Assuming that $m$ and $M$ are independent conditional on the genomic context, $\mathrm{p}(m,M \mid C) = \mathrm{p}(m \mid C) \mathrm{p}(M \mid C)$, which we can use Bayes' rule to further decompose as

@@

\subsection{Evaluation methods}
ROC
PRC
ICI. We used loess smoothing "loess" function in R with span = 0.5.
\begin{tiny}
\begin{verbatim}

@@

\begin{figure*}
  \begin{center}
  \includegraphics{figures/fig_wes.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome.
  \textbf{(a)} Precision recall curves and \textbf{(c)} Reciever operating characteristic curves for 3 mutation signatures.
  Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the \batcave model.
  A perfectly calibrated model would generate the diagonal line.\bkmcomment{change the axis on b and d to be the same as the steyerberg paper. much clearer}}
\label{NAR-wgs_fig}
\end{figure*}
\end{document}
